% This file is part of the Digital Assyriologist.  Copyright
% (c) Steve Tinney, 1994, 1995.  It is distributed under the
% Gnu General Public License as specified in /da/doc/COPYING.
%
% $Id: polybase.tex,v 0.3 1996/02/17 02:58:37 s Exp $

% Basic polyglot definitions for DA format: user extensions should
% be placed in polyuser.tex (probably in tex/inputs/polyuser.tex or the
% like).
\polyglot{obverse}{Obverse}{Face}{Vorderseite}{Recto}{Recto}
\polyglot{reverse}{Reverse}{Revers}{Rñckseite}{Verso}{}
\polyglot{leftedge}{Left Edge}{Tranche gauche}{Linker Rand}{}{}
\polyglot{rightedge}{Right Edge}{Tranche droite}{Rechter Rand}{}{}
\polyglot{topedge}{Top Edge}{Tranche supÅrieure}{Oberer Rand}{}{}
\polyglot{bottomedge}{Bottom Edge}{Tranche infÅrieure}{Unterer Rand}{}{}
\polyglot{column}{Column}{Colonne}{Spalte}{}{}
\polyglot{side}{Side}{Face}{Seite}{}{}
\polyglot{tablet}{Tablet}{Tablette}{Tafel}{}{}
\polyglot{envelope}{Envelope}{Envelope}{Hñlle}{}{}
\polyglot{source}{Source}{Source}{Quelle}{}{}
\polyglot{part}{Part}{Section}{Teil}{}{}

\polyglot{obverseabb}{obv.}{face}{vs.}{r.}{}
\polyglot{reverseabb}{rev.}{rev.}{rs.}{v.}{}
\polyglot{leftedgeabb}{l.e.}{tr. gauche}{l. Rand}{}{}
\polyglot{rightedgeabb}{r.e.}{tr. droite}{r. Rand}{}{}
\polyglot{topedgeabb}{t.e.}{tr. sup.}{o. Rand}{}{}
\polyglot{bottomedgeabb}{b.e.}{tr. inf.}{u. Rand}{}{}
\polyglot{columnabb}{col.}{col.}{sp.}{}{}
\polyglot{sideabb}{side}{face}{seite}{}{}
\polyglot{tabletabb}{tab.}{tab.}{taf.}{}{}
\polyglot{sourceabb}{Src.}{Source}{Quelle}{}{}
\polyglot{partabb}{part}{sect.}{teil}{}{}

\polyglot{appendix}{Appendix}{Appendice}{Appendix}{}{}
\polyglot{chapter}{Chapter}{Chapitre}{Kapitel}{}{}
\polyglot{introduction}{Introduction}{Introduction}{}{}{}
\polyglot{credits}{Credits}{}{}{}{}
\polyglot{previousliterature}{Previous Literature}{}{}{}{}

\polyglot{source}{Source}{}{}{}{}
\polyglot{museumnumbers}{Museum Numbers}{}{}{}{}
\polyglot{andpublication}{and Publications}{}{}{}{}
\polyglot{prov}{Prov.}{}{}{}{}
\polyglot{description}{Description}{}{}{}{}
\polyglot{lines}{Lines}{}{}{}{}

\endinput

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

$Log: polybase.tex,v $
Revision 0.3  1996/02/17 02:58:37  s
change Kante to Rand

add Fr/Ge for source

% Revision 0.2  1995/02/14  03:07:57  s
% fixed tablet def and added envelope def
%
% Revision 0.1  1994/12/12  03:56:05  s
% initial checkin
%
